### 2022-09-25 LaTeX/MSGARCH.tex
Checkpoint

% ACRONYMS 
\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}
\newacro{GED}{Generlized Error Distribution}

@@

\subsection{Experiment description}
We compare the performance of 3 models: 
1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
2. A markov-switching model without indicators
3. A markov-switching model with indicators

@@

@@

\subsection{Results}

% latex table generated in R 4.1.2 by xtable 1.8-4 package
% Thu Sep 22 19:29:22 2022
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & MSSR1 & MSSR2 & GARCH \\ 
  \hline
$\alpha\_1$ & 0.17 & 0.00 & 0.01 \\ 
  alpha1\_1 & 0.02 & 0.02 & 0.03 \\ 
  alpha2\_1 & 0.21 & 0.08 & 0.08 \\ 
  beta\_1 & 0.75 & 0.94 & 0.92 \\ 
  nu\_1 & 1.05 & 1.53 & 6.19 \\ 
  xi\_1 & 0.86 & 0.96 & 0.93 \\ 
   \hline
\end{tabular}
\end{table}

@@

>>>>

% ACRONYMS 
\newacro{GARCH}{General Autoregressive Conditional Heteroskedasticity}
\newacro{ARCH}{Autoregressive Conditional Heteroskedasticity}
\newacro{ARMA}{AutoRegressive Moving Average}
\newacro{SGED}{Skewed Generlized Error Distribution}
\newacro{GED}{Generlized Error Distribution}
\newacro{MSE}{mean-square error}
\newacro{MAE}{mean-absolute error}
\newacro{RMSE}{root-mean-square error}

@@

\subsection{Experiment description}
We compare the performance of 2 models a stand-alone GARCH model and a MSGARCH model

@@

\subsubsection{Performance Measures}
When measuring the performance one has to be careful not to compare the square root variance forecasts $\sqrt{h_t}$ with the absolute returns $\sqrt{y_t^2} = | y_t |$ as these would be biased due to Jensen's inequality: Our model tries to achieve $\mathbb{V}(y) =\mathbb{E}(y^2) = h$ and $\mathbb{E}(| y |) \neq \sqrt{h}$. Instead the variance $h_t$ should be compared to the squared returns $y_t^2$.

The actual measures we employ are the following: \ac{MSE}, \ac{MAE}, \ac{RMSE}

@@

\subsection{Results}
\subsubsection{Analysis of Model Parameters}
In \cref{tab:model-params} the model parameters are displayed, which were fitted using a maximum likelihood estimator and the training set.

% latex table generated in R 4.1.2 by xtable 1.8-4 package
% Thu Sep 22 19:29:22 2022
\begin{table}[ht]
\label{tab:model-params}
\centering
\begin{tabular}{rrrr}
  \hline
 & MSSR1 & MSSR2 & GARCH \\ 
  \hline
$\alpha\_1$ & 0.17 & 0.00 & 0.01 \\ 
  alpha1\_1 & 0.02 & 0.02 & 0.03 \\ 
  alpha2\_1 & 0.21 & 0.08 & 0.08 \\ 
  beta\_1 & 0.75 & 0.94 & 0.92 \\ 
  nu\_1 & 1.05 & 1.53 & 6.19 \\ 
  xi\_1 & 0.86 & 0.96 & 0.93 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & mse & mae & rmse & bias \\ 
  \hline
MSGARCH\_h1 & 24.2096 & 1.5169 & 4.9203 & 0.0195 \\ 
  GARCH\_h1 & 24.9891 & 1.5415 & 4.9989 & 0.0441 \\ 
  MSSR1\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
  MSSR\_h1 & 25.2808 & 1.5446 & 5.0280 & 0.0380 \\ 
  Avg & 33.6508 & 1.8815 & 5.8009 & -0.0301 \\ 
   \hline
\end{tabular}
\end{table}
